The K2 Bright Star Survey

### 2019-05-21 paper/ms.tex
proper names are resolved as normal designations

Using the Sydney pipeline \citep{Huber2009} with modifications to the extraction of \Dnu detailed in \citep{Yu2018}, we extract the global asteroseismic parameters \numax and \Dnu for all 31 giants for which oscillations are detected. These parameters are listed in Table~\ref{rgs}. High precision spectroscopy of these stars would permit detailed stellar modelling and the extraction of precise elemental abundances, which would make these stars valuable as benchmarks for large spectroscopic surveys or testing detailed stellar models. This sample would be a valuable addition to the~36 Gaia FGK benchmark stars \citep{gaiabenchmark1,gaiabenchmark3,2018RNAAS...2c.152J}, the 23 BRITE-Constellation asteroseismic giants \citep{Kallinger2019}, and the~33 \kepler Smear Campaign spectroscopic benchmark red giants (Pope et al., 2019, under review).

@@

% do k2 smear after that
The sample of K2 bright stars presented here only includes those with halo apertures. While some others are available conventionally, many were not assigned target pixels and were not downloaded at all. Smear photometry has been used to recover the brightest otherwise-unobserved stars in nominal \kepler (Pope et al., under review), and this can also be done in K2, although the sample is much smaller due to allocation of halo apertures and the systematics correction is more challenging. A natural extension of both pieces of work would be to produce smear light curves of all bright stars without halo apertures in K2, which would finally make the \kepler extended mission magnitude-complete at the bright end.

>>>>

Using the Sydney pipeline \citep{Huber2009} with modifications to the extraction of \Dnu detailed in \citep{Yu2018}, we extract the global asteroseismic parameters \numax and \Dnu for all 31 giants for which oscillations are detected. These parameters are listed in Table~\ref{rgs}. High precision spectroscopy of these stars would permit detailed stellar modelling and the extraction of precise elemental abundances, which would make these stars valuable as benchmarks for large spectroscopic surveys or testing detailed stellar models. This sample would be a valuable addition to the~36 Gaia FGK benchmark stars \citep{gaiabenchmark1,gaiabenchmark3,2018RNAAS...2c.152J}, the 23 BRITE-Constellation asteroseismic giants \citep{Kallinger2019}, and the~33 \kepler Smear Campaign spectroscopic benchmark red giants (Pope et al., 2019, accepted ApJS).

@@

% do k2 smear after that
The sample of K2 bright stars presented here only includes those with halo apertures. While some others are available conventionally, many were not assigned target pixels and were not downloaded at all. Smear photometry has been used to recover the brightest otherwise-unobserved stars in nominal \kepler (Pope et al., 2019, accepted ApJS), and this can also be done in K2, although the sample is much smaller due to allocation of halo apertures and the systematics correction is more challenging. A natural extension of both pieces of work would be to produce smear light curves of all bright stars without halo apertures in K2, which would finally make the \kepler extended mission magnitude-complete at the bright end.
